### 2017-07-24 README.Rmd
misc CRAN updates

```{r setup, echo = FALSE}

@@

[![Travis Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/visdat/master.svg)](https://codecov.io/github/njtierney/visdat?branch=master)

@@

```{r installation, eval = FALSE}
# install.packages("devtools")

@@

>>>>

```{r, echo = FALSE}

@@

[![Travis Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/visdat/master.svg)](https://codecov.io/github/njtierney/visdat?branch=master)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)

@@

```{r eval = FALSE}
# install.packages("devtools")

@@

There are also experimental which are described in more detail in the vignette ["Experimental Features of visdat](http://www.njtierney.com/visdat/articles/experimental_features.html).
